### 2015-05-11 Body/LitReview/LitReview.tex
Getting the ball rolling

To evaluate how technology has evolved in recent years, we begin with existing reviews on the subject. \citet{chance2007} reflect on how the statistics education reform movement impacted the role of technology. They evaluated that, as of 2007, technology was being widely used to help with educational administration through course management software. Currently, the most popular learning platforms include Blackboard \citep{Blackboard}, Moodle \citep{Moodle} and Desire2Learn \citep{Desire2Learn} that account for 44\%, 23\% and 11\% market share, respectively \citep{CampusComputing}. Chance et al. found that general purpose statistical analysis software, such as \textit{R} \citep{R}, \textit{SAS} \citep{SAS}, \textit{SPSS} \citep{SPSS}, \textit{STATA} \citep{STATA} and \textit{Minitab} \citep{Minitab}, had gained a large footing within statistics curricula to support the increased focus on applied data analysis. They also found that software and hardware had developed specifically to facilitate the change in content and pedagogy \citep{chance2007}. \citet{Rubin2007} evaluated the changing trends of technology in statistics education from 1992 to 2007. She illustrated how several software programs were implemented to introduce new data and graphical displays to the statistics classroom. She concluded that although new data sources and user interfaces allow for a more advanced methods for statistics education, problems with student understanding persist, stating ``a general caution for readers; as amazing and inspiring as these technologies may seem, none of them can have any educational effect without carefully constructing curriculum and talented teaching'' \citep[p.2]{Rubin2007}.

>>>>

To evaluate how technology has evolved in recent years, we begin with existing reviews on the subject. \citet{chance2007} reflect on how the statistics education reform movement impacted the role of technology. They evaluated that, as of 2007, technology was being widely used to help with educational administration through course management software. Currently, the most popular learning platforms include Blackboard \citep{Blackboard}, Moodle \citep{Moodle} and Desire2Learn \citeyearper{Desire2Learn} that account for 44\%, 23\% and 11\% market share, respectively \citep{CampusComputing}. Chance et al. found that general purpose statistical analysis software, such as \textit{R} \citep{R}, \textit{SAS} \citep{SAS}, \textit{SPSS} \citep{SPSS}, \textit{STATA} \citep{STATA} and \textit{Minitab} \citep{Minitab}, had gained a large footing within statistics curricula to support the increased focus on applied data analysis. They also found that software and hardware had developed specifically to facilitate the change in content and pedagogy \citep{chance2007}. \citet{Rubin2007} evaluated the changing trends of technology in statistics education from 1992 to 2007. She illustrated how several software programs were implemented to introduce new data and graphical displays to the statistics classroom. She concluded that although new data sources and user interfaces allow for a more advanced methods for statistics education, problems with student understanding persist, stating ``a general caution for readers; as amazing and inspiring as these technologies may seem, none of them can have any educational effect without carefully constructing curriculum and talented teaching'' \citep[p.2]{Rubin2007}.

### 2015-05-11 thesis.Rnw
Getting the ball rolling

% Template file for a standard thesis
\documentclass[11pt]{isuthesis}
%---------------------------------------------------
% \usepackage{color}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{wrapfig,float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{ulem}
\usepackage[section]{placeins}
\usepackage{sidecap}
\usepackage{multirow}
\usepackage{bbm}
\usepackage{rotating}
\usepackage[referable]{threeparttablex}
\usepackage{footnote} % table footnotes
\usepackage{multicol}
%---------------------------------------------------

@@

% Bibliography without numbers or labels
\usepackage{natbib}
\bibliographystyle{apa}

@@

\section{Introduction}

Chapter 3 studies the development of a \texttt{shiny} \citep{shiny} application to connect students to large data; thus literature on developing and evaluating

% <<litReview, child='Body/LitReview.Rnw'>>=
% @
% \chaptocbreak
% <<sineIllusion, child='Body/SineIllusion.Rnw'>>=
% @
% \chaptocbreak
% <<lieFactorSine, child='Body/LieFactorSine.Rnw'>>=
% @
% \chaptocbreak
% <<visualaReasoning, child='Body/VisualAptitude.Rnw'>>=
% @
% \chaptocbreak
% <<featureHierarchy, child='Body/FeatureHierarchy.Rnw'>>=
% @
% <<Conclusion, child='Body/Conclusion.Rnw'>>=
% @
%-------------------------------------------------------------------------------
% \include{Appendix/appendix1}
% \include{Appendix/appendix2}
%-------------------------------------------------------------------------------
\include{Reference/bibtex}
\bibliography{Reference/references}
%\include{Reference/biblio} % Not used... stick with bibtex
\end{document}

>>>>

% Template file for a standard thesis
\documentclass[11pt]{isuthesis}
%---------------------------------------------------
% \usepackage{color}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{wrapfig,float}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{ulem}
\usepackage[section]{placeins}
\usepackage{multirow}
\usepackage{bbm}
\usepackage{rotating}
\usepackage[referable]{threeparttablex}
\usepackage{footnote} % table footnotes
\usepackage{multicol}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{fullpage}
\usepackage{graphicx,float,wrapfig,subfig,tabularx,ulem}
\graphicspath{{Figure/}}
%\usepackage{csquotes}
\usepackage{color}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{url}
\usepackage{bbm}

%---------------------------------------------------

@@

% Bibliography without numbers or labels
\usepackage{natbib}
\bibliographystyle{asa}

@@

<<litReview, child='Body/LitReview/LitReview.Rnw'>>=
@
 \chaptocbreak
 <<TISEPaper, child='Body/CurriculumStudy/CurriculumStudy.Rnw'>>=
 @
% \chaptocbreak
% <<lieFactorSine, child='Body/LieFactorSine.Rnw'>>=
% @
% \chaptocbreak
% <<visualaReasoning, child='Body/VisualAptitude.Rnw'>>=
% @
% \chaptocbreak
% <<featureHierarchy, child='Body/FeatureHierarchy.Rnw'>>=
% @
% <<Conclusion, child='Body/Conclusion.Rnw'>>=
% @
%-------------------------------------------------------------------------------
% \include{Appendix/appendix1}
% \include{Appendix/appendix2}
%-------------------------------------------------------------------------------
\include{Reference/bibtex}
\bibliography{Reference/references}
%\include{Reference/biblio} % Not used... stick with bibtex
\end{document}
